Duplicate Question Detection using Online Learning

### 2016-11-27 paper/main.tex
fix another table

\begin{table}[h!]
\centering
\caption{Recall rate for both datasets using different supervised models.}
 \begin{tabular}{|l r r|} 
 \hline
 Dataset & Model & Recall Rate  \\ [0.5ex] 
 \hline\hline
 Stackoverflow & Random Forest & 76.87\%  \\
 Stackoverflow & Logistic Regression & 37.12\%  \\
 \hline
  Reddit & Random Forest & 80.59\%  \\
  Reddit & Logistic Regression & 10.84\%  \\
 \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{Recall rate for both datasets using different supervised models.}
 \begin{tabular}{l l r} 
 \hline
 Dataset & Model & Recall Rate  \\ 
 \hline
 Stackoverflow & Random Forest & 76.87\%  \\
 Stackoverflow & Logistic Regression & 37.12\%  \\
   Reddit & Random Forest & 80.59\%  \\
  Reddit & Logistic Regression & 10.84\%  \\
 \hline
\end{tabular}
\end{table}
